---
title: ACS Data analysis
author: 
  - Group 23
date: 03-10-2024
date-format: long
format: pdf
number-sections: true
---

# Obtaining the data
1. Go the Ipums website, register using your information. \newline
2. Locate Ipums USA, click "visit site". \newline
3. In a blue box, click "Get Data". \newline
4. On the left side, click "Select Sample", and only select 2022 ACS. Then click "Submit Sample Selection. \newline
5. 

```{r}
#| echo: false
#| message: false
data <- read.csv("usa_00001.csv")
library(dplyr)
```

# Number of Phd in each state


# Estimated respondent Vs. Actual respondent

The ratio was calculated by 391,171 divided by the total number of respondent with a phd in California.
```{r}
#| echo: false
#| message: false
#| fig-cap: Estimated respondent Vs. Actual respondent

library(knitr)
state <- data %>% group_by(STATEICP) %>% summarise(total = n())
doctor <- data %>% filter(EDUC >=8) %>% group_by(STATEICP) %>% summarise(number_doc = n())

ratio <- 138590/391171
predict_total_number <- doctor %>% reframe(STATEICP, Estimated_respondent = round(number_doc/ratio))
compare <- predict_total_number %>% mutate(Actual_respondent = state$total)
kable(compare)

```

```{r}

```

